\begin{thebibliography}{99}

\bibitem{etl} Petr ŠKODA, Jakub KLÍMEK, Martin NEČASKÝ, LinkedPipes ETL REST API. In: Github [online], GitHub Inc., 28 Oct 2017, [cit. 2020-12-06], Available from: https://github.com/linkedpipes/etl/wiki/LinkedPipes-ETL-REST-API

\bibitem{bootstrap} Bootstrap · The most popular HTML, CSS, and JS library in the world [online], Twitter, Inc., [cit. 2020-12-06], Available from: \url{https://getbootstrap.com/}

\bibitem{react} React – A JavaScript library for building user interfaces [online], Facebook Inc., [cit. 2020-12-06], Available from: \url{https://reactjs.org/}

\bibitem{wcag} Web Content Accessibility Guidelines (WCAG) Overview | Web Accessibility Initiative (WAI) | W3C [online], W3C, [cit. 2020-12-06], Available from: \url{https://www.w3.org/WAI/standards-guidelines/wcag/}

\bibitem{materialandroid} Develop - Android - Material Design [online], Google LLC, [cit. 2020-12-06], Available from: \url{https://material.io/develop/android}

\bibitem{design} Android Developers [online], Google LLC, [cit. 2020-12-06], Available from: \url{https://developer.android.com/design}

\bibitem{material} Design - Material Design [online], Google LLC, [cit. 2020-12-06], Available from: \url{https://material.io/design}

\bibitem{droidcon} MUNTENESCU, Florina and Touchlab, Droidcon NYC 2016 - A Journey Through MV Wonderland (updated), Youtube [video], Youtube LLC, 2016, [cit. 2020-12-06], Available from: \url{https://youtu.be/QrbhPcbZv0I}

\bibitem{mvp} LEIJDEKKERS, Peter and ANZ Coders, Android MVP vs MVVM and the winner is..., Youtube [video], Youtube LLC, 2018, [cit. 2021-03-26], Available from: \url{https://youtu.be/ugpC98LcNqA}

\bibitem{room} Save data in a local database using Room | Android Developers [online], Google LLC, [cit. 2021-04-10], Available from: \url{https://developer.android.com/training/data-storage/room}

\bibitem{livedata} LiveData Overview | Android Developers [online], Google LLC, [cit. 2021-04-10], Available from: \url{https://developer.android.com/topic/libraries/architecture/livedata}

\bibitem{retrofit} Retrofit [online], Square, Inc., [cit. 2021-04-10], Available from: \url{https://square.github.io/retrofit/}

\bibitem{varvet} Android QR Code Reader Made Easy — Varvet [online], Varvet, [cit. 2021-04-10], Available from: \url{https://www.varvet.com/blog/android-qr-code-reader-made-easy/}

\bibitem{draggable} DraggableView [online], Muhammad Wahyudin, [cit. 2021-04-10], Available from: \url{https://github.com/hyuwah/DraggableView}

\bibitem{realm} Home | Realm.io [online], MongoDB, Inc., [cit. 2020-12-06], Available from: \url{https://realm.io/}

\bibitem{objectbox} ObjectBox - Edge Database for Mobile and IoT [online], ObjectBox Ltd., [cit. 2020-12-06], Available from: \url{https://objectbox.io/}

\bibitem{volley} Volley overview | Android Developers [online], Google LLC, [cit. 2020-12-06], Available from: \url{https://developer.android.com/training/volley}

\bibitem{rxjava} RxJava Contributors, RxJava: Reactive Extensions for the JVM. In: Github [online], GitHub Inc., [cit. 2020-12-06], Available from: \url{https://github.com/ReactiveX/RxJava}

% \bibitem{ref} title [online], creator, [cit. 2020-12-06], Available from: \url{link}

\end{thebibliography}