In this section, an overview of possible existing solutions can be found. There will be a table with comparisons of those solutions by the end of this chapter.

\section{Responsive web app}
The web front-end can be used by any device possessing a web browser.
Users are not obligated to download any application, which also means they do not have to update anything.
The responsive web app only works with one server instance.
On an Android device, the web app responds slower to screen rotation and animations often lag.
Users have to be online, even just for browsing execution history or viewing a pipeline list.
The responsive web app is also browser dependent.

\section{Summary}
In this section, existing solutions are being compared with each other (see \autoref{tab:existingSolutions}), resulting in a decision if there is a need to create a new application.

\begin{table}[ht]\centering
\caption[Existing solutions]{Features of existing solutions}\label{tab:existingSolutions}
\begin{tabular}{l|l|l}
\hline
\textbf{Feature} & \textbf{Android App} & \textbf{Web App} \\ \hline
Can work with multiple server instances & + & - \\ \hline
Works on any device & - & + \\ \hline
Does not need to be downloaded & - & + \\ \hline
Smooth UI & + & - \\ \hline
Can view stuff while offline & + & - \\ \hline
\end{tabular}
\end{table}

The comparison indicates that the web application is missing at least one critical feature, that is not being able to work with multiple server instances, thus there is a need for the creation of a new application.